### 2016-09-08 padics/hw2.tex
updating hw

@@

\item Suppose that $F$ is a field and $|\ |$ is a non-Archemedian absolute value on $F$. if $c\in F$
and $r$ is a positive real number, we define the \textit{open ball (or disk) centered at c of radius r}
by
\[
B(c,r)=\{x\in F:|x-c|<r\}.
\]
If $d\in B(c,r)$, prove that $B(c,r)=B(d,r)$.
\end{enumerate}
\end{document}

>>>>

\geometry{margin=1in}

@@

	\item Suppose that $F$ is a field and $|\ |$ is a non-Archemedian absolute value on $F$. If $c\in F$
	      and $r$ is a positive real number, we define the \textit{open ball (or disk) centered at c of radius r}
	      by
	      \[
	      	B(c,r)=\{x\in F:|x-c|<r\}.
	      \]
	      If $d\in B(c,r)$, prove that $B(c,r)=B(d,r)$.
	      \begin{quote}
	      	\textit{\textbf{Proof:}} Suppose $x\in B(d,r)$. Then
			\begin{align*}
				|x-d| &= |x-d-c+c|\\
				&= |x-c + c-d|\\
				&\leq \text{max}\{|x-c|,|c-d|\}\\
				&= \text{max}\{|x-c|,|d-c|\}\\
				&\leq\text{max}\{|x-c|,r\}.
			\end{align*}
			Suppose $|x-d|\leq |x-c|$. Then the value $|x-d|$ is always within the disk $B(c,r)$.\\\\
			Suppose $x\in B(c,r)$. Then
			\begin{align*}
				|x-c| &= |x-c-d+d|\\
				&= |x-d + d-c|\\
				&\leq \text{max}\{|x-d|,|d-c|\}\\
				&<\text{max}\{|x-d|,r\}.
			\end{align*}
			Suppose max$\{|x-d|,r\} = |x-d|$. Then $|x-c|$ is always within the disk $B(d,r)$.
	      \end{quote}
\end{enumerate}
\end{document}
